Choosing a Population Genomics Approach

### 2021-11-05 choosing-population-genetics.Rmd
Added new reference bib file

---
bibliography: bibtexlib.bib
title: Choosing a Population Genomics Approach 
---

@@

### 1) High coverage individual whole genome resequencing (hcWGS)  {.unlisted .unnumbered}
**Whole-genome resequencing (WGS)** is where whole genomes of multiple individuals are sequenced and mapped to an assembled reference genome in order to compare variable sites between individuals or populations. **Coverage depth** refers to the average number of sequencing reads per region of the genome. With more sequencing reads at a region (higher coverage depth), errors that arise during sequencing have a smaller impact on accurately identifying variable sites (termed "genotyping") (cite).

@@

![Figure 1 from Lou et al. 2021 comparing the distribution of sequencing reads mapped to a reference genome.](images/mec16077-fig-0001-m.jpg)

@@

References:

* Matz 2018[@zeeberg2004mistaken]: great intro to ecological genomics methods in species with few to no prior genomic resources, accessible to those just getting started.  
* Fuentes-Pardo and Ruzzante 2017: a VERY thorough review of the different approaches to generating population genomics data, with non-model species in mind. Some of the content about relative cost and available software is a little dated, but otherwise a very valuable reference.   
* Benjelloun et al 2019: empirical comparison of high coverage WGS, low coverage WGS, random variants (eg. from RADseq), exome capture, and commercial SNP chip for mammals (genome size=2.6Gb). For neutral genomic diversity, found 5k-10k random variants were enough to accurately estimate, but comercial panales/exome capture had acertainment bias. To detect selection and accurate estimates of LD, at least 1M variants were required. For the studied species, 5x coverage was just as accurate as 12x coverage. Low coverage WGS (< 5x) should use genotype likelihood methods, however the rate of false positives for heterozygotes is higher than classic genotyping methods at higher coverage.  
* Dorant et al. 2019: Case study comparing Poolseq vs. reduced representation seq (GBS) vs Rapture (targeted capture of RAD loci) for inferring population structure with weak genetic differentiation. All three detected same weak pop structure pattern, but Poolseq gave Fst values 3-5x higher than Rapture/GBS.

>>>>

---
bibliography: RCN_site-Nov05.bib
title: Choosing a Population Genomics Approach 
---

@@

### 1) High coverage individual whole genome resequencing (hcWGS)  {.unlisted .unnumbered}
**Whole-genome resequencing (WGS)** is where whole genomes of multiple individuals are sequenced and mapped to an assembled reference genome in order to compare variable sites between individuals or populations. **Coverage depth** refers to the average number of sequencing reads per region of the genome. With more sequencing reads at a region (higher coverage depth), errors that arise during sequencing have a smaller impact on accurately identifying variable sites (termed "genotyping") [@Fuentes-Pardo2017-nu].

@@

![Figure 1 from [@Lou2021-me] comparing the distribution of sequencing reads mapped to a reference genome.](images/mec16077-fig-0001-m.jpg)

@@

Review articles:

* [@Matz2018-vl]: great intro to ecological genomics methods in species with few to no prior genomic resources, accessible to those just getting started.  
* [@Fuentes-Pardo2017-nu]: a VERY thorough review of the different approaches to generating population genomics data, with non-model species in mind. Some of the content about relative cost and available software is a little dated, but otherwise a very valuable reference.   
* [@Lou2021-me]: Great recent primer on low coverage WGS and how it compares to RADseq and Poolseq.

Empiracal comparisions:

* [@Benjelloun2019-dq]: empirical comparison of high coverage WGS, low coverage WGS, random variants (eg. from RADseq), exome capture, and commercial SNP chip for mammals (genome size=2.6Gb). For neutral genomic diversity, found 5k-10k random variants were enough to accurately estimate, but comercial panales/exome capture had acertainment bias. To detect selection and accurate estimates of LD, at least 1M variants were required. For the studied species, 5x coverage was just as accurate as 12x coverage. Low coverage WGS (< 5x) should use genotype likelihood methods, however the rate of false positives for heterozygotes is higher than classic genotyping methods at higher coverage.  
* [@Dorant2019-fb]: Case study comparing Poolseq vs. reduced representation seq (GBS) vs Rapture (targeted capture of RAD loci) for inferring population structure with weak genetic differentiation. All three detected same weak pop structure pattern, but Poolseq gave Fst values 3-5x higher than Rapture/GBS.
